Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-24 PAPER.tex
updated KDE plots to include pos and neg axes

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
not exhibit loss. The peculiar `signal gain' tail seen at low injection is driven by the cross-terms in Equation \eqref{eq:pout_expand}, also shown by the red curve in the right panel in Figure \ref{fig:sigloss_terms}.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
given injection level P$_{in}$. The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $P_{\rm out}$ converges to the data level.
}
\label{fig:Pr_vs_Pin}
\end{figure}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
not exhibit loss. The peculiar `signal gain' tail seen at low injection is driven by the cross-terms in Equation \eqref{eq:pout_expand}, also shown by the red curve in the right panel in Figure \ref{fig:sigloss_terms}.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
given injection level P$_{in}$. The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
}
\label{fig:Pr_vs_Pin}
\end{figure}
